---
title: "nes_diet: Diet Composition for Small Pelagic Fishes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{nes_diet_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Loading Data

```{r setup}
library(bonanza)
library(tidyverse)

diet <- na.omit(bonanza::nes_diet) %>%
  filter(preyCount < 50000)
```

## Initial Plots

Creating scatterplots of preyCount versus two predictors of interest:

```{r plots, fig.width=7, fig.height=5}

ggplot(data = diet, aes(x = forkLength, y = preyCount)) +
 		 geom_point()

ggplot(data = diet, aes(x = average_depth, y = preyCount)) +
 		 geom_point()
```

## Grouped Histograms

Extracting data concerning a specific prey species:

```{r cor}

sub <- diet %>%
  filter(scientificName_preyTaxon == "Centropages")

```

Creating histogram of preyCount, grouped by predator species:

```{r plot2, fig.width=7, fig.height=5}
ggplot(sub, aes(x = preyCount)) +
  geom_histogram(aes(color = vernacularName, fill = vernacularName),
                 position = "identity", bins = 10, alpha=I(0.3)) +
  scale_color_manual(values = c("#00AFBB", "#E7B800", "#FADB7D", "#E38566", "#F68FFF")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FADB7D", "#E38566", "#F68FFF")) +
  ggtitle("Histogram of Size(mm) by Site")

```
Choosing another species:

```{r plot3, fig.width=7, fig.height=5}

sub <- diet %>%
  filter(scientificName_preyTaxon == "Calanoida")

ggplot(sub, aes(x = preyCount)) +
  geom_histogram(aes(color = vernacularName, fill = vernacularName),
                 position = "identity", bins = 10, alpha=I(0.3)) +
  scale_color_manual(values = c("#00AFBB", "#E7B800", "#FADB7D", "#E38566", "#F68FFF")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FADB7D", "#E38566", "#F68FFF")) +
  ggtitle("Histogram of Size(mm) by Site")

```

### Citation

Suca, J.J. 2019. Diet Composition for Small Pelagic Fishes across the Northeast U.S. Continental Shelf from 2013-2015 ver 2. Environmental Data Initiative. https://doi.org/10.6073/pasta/4c1ef62808519d46b14a8493616e1580 (Accessed 2021-03-07).

### Raw Data Processing

See "data-raw/nes_diet.R".
